Urbanization and Public Transportation of Los Angeles

### 2023-10-26 Paper.Rmd
Update Paper.Rmd

---
title: "Urbanization and Public Transportation of Los Angeles"
author: "Kainoa Kanter, Julian Jacobson, Aidan Lastname"
date: "2023-10-25" # Change to date when we submit
output:
    pdf_document:
        extra_dependencies: ['amsmath']
---

>>>>

---
title: "Urbanization and Public Transportation of Los Angeles"
bibliography: master.bib
author: 
  name: "Kainoa Kanter, Julian Jacobson, Aidan Lastname"
  affiliation: "Math 28, Professor Smith, Santa Monica College"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
output:
    pdf_document:
        extra_dependencies: ['amsmath']
---
